Dynamic Discourse and Donkeys: Using Monoids for Language Semantics in Practice

### 2013-04-28 paper.tex
Works very well now, and it's clean too!

@@

>>>>

% Samson suggests using the word 'Computational'

@@

\begin{align}
&\exists a \cdot farmer(a) \rightarrow \exists g \cdot donkey(g) \cdot beat(a,g) \\
&\exists a \cdot farmer(a) \cdot (\exists b \cdot donkey(b) \cdot own(a,b)) \rightarrow beat(a,b) \\
&\exists a \cdot farmer(a) \cdot own(a,b) \cdot beat(a,b) \rightarrow a\_donkey(b) \\
&\exists c \cdot farmer(c) \cdot (own(c,a) \cdot beat(c,a)) \rightarrow a\_donkey(a) \\
&\exists a \cdot man(a) \cdot come\_in(a) \cdot (\exists i \cdot dog(i) \cdot see(a,i) \cdot smile(a)) \\
&\exists a \cdot farmer(a) \cdot (\exists b \cdot donkey(b) \cdot (own(a,b) \cdot beat(a,b))) \\
&\exists a \cdot donkey(a) \rightarrow \exists g \cdot horse(g) \cdot (\exists o \cdot eq\_on\_of(o,a,g) \rightarrow \exists v \cdot song(v) \cdot sing(o,v)) \\
&\exists a \cdot farmer(a) \cdot (\exists p \cdot donkey(p) \cdot (starve(a,p) \cdot beat(a,p))) \\
&\exists a \cdot farmer(a) \cdot (\exists g \cdot horse(g) \cdot starve(a,g) \cdot (\exists ac \cdot donkey(ac) \cdot beat(a,ac))) \\
&\exists a \cdot man(a) \cdot walk(a) \rightarrow talk(a) \\
&a\_mother\_of\_five(a) \\
&\neg (\exists a \cdot man(a) \cdot walk\_in\_the\_park(a)) \cdot yodel(a) \\
&\exists a \cdot farmer(a) \cdot (\exists g \cdot donkey(g) \cdot (\exists o \cdot eq\_on\_of(o,a,g) \rightarrow \exists v \cdot friend(v) \cdot visit(o,v))) \\
&\neg (\exists a \cdot man(a) \cdot walk\_in\_the\_park(a)) \cdot (\exists r \cdot donkey(r) \cdot (yodel(a,r) \cdot beat(a,r))) \\
&\exists a \cdot farmer(a) \cdot (\exists b \cdot donkey(b) \cdot own(a,b)) \cdot (brown(b) \cdot beat\_every\_day(a,b)) \\
&\exists a \cdot (farmer(a) \cdot entrepreneur(a)) \cdot (\exists p \cdot donkey(p) \cdot beat(a,p))\end{align}
